\documentclass[DIV=18,parskip=half, a4paper]{scrartcl}
\usepackage{fontspec}
\setmainfont{Tex Gyre Schola}
\begin{document}
\section*{Overview}
Hi, I'm Mike and I'd like to tell you about my newest game, Eruption. 

Eruption is a volcano-themed dexterity game for two to six players.

\section*{Set Up}
To set up the game, you will first choose a starting player.

Then each other player will place a rubber band flat on the table.

These rubber bands represent volcanoes.

Finally, you will place ten black cubes and one white cube into each of the volcanoes.

These cubes represent lava.

\section*{Gameplay}
On your turn, you will place a cube into one of the volcanoes.

You may only use one hand at a time to do so.

You must place your new cube so that it is touching a white cube.

\subsection*{Eruptions}
As you place more cubes into the volcanoes, the rubber bands will stretch.

As they do, they pressure builds and adding more cubes becomes progressively more difficult.

Eventually (BANG), a volcano will erupt, spraying its lava cubes all over the table.

If that happens on your turn, you and the volcano that erupted are removed from the game.

\subsection*{Winning}
You win if all of your opponents have been eliminated.


\section*{Conclusion}
That's all there is to it! 

Eruption is a compact dexterity game.

It uses standard components to create a unique game experience that is engaging and challenging.

Dynamic eruptions that ensure that every game ends with a bang.
\end{document}
